VISUALIZATION OF THE RIEMANN-LIOUVILLE FRACTIONAL INTEGRAL \\ [3pt] IN ``FCAA'' JOURNAL

### 2019-09-20 fractional/FCAA/Authors Kit (Updated)/FCAA-template-for-authors.tex
added worked example - not finished

 \title[VISUALIZATION OF THE FRACTIONAL INTEGRAL \dots]{VISUALIZATION OF THE RIEMANN-LIOUVILLE FRACTIONAL INTEGRAL \\ [3pt] IN ``FCAA'' JOURNAL}
 \author[\normalsize V. Kiryakova, S. Author]{\normalsize Virginia Kiryakova $^1$, Second Author $^2$}

@@

Ackerman et al. used the notion of non-rectangular integration strips to define the so called Cavalieri integral. The area of a non-rectangular 
integration strip is calculated using Cavalieri's principle. The formal definition of the Cavalieri integral is given in Definition~\ref{def:cav_integral}.
It is, however, our experience that Definition~\ref{def:cav_integral} is hard to assimilate if it is encounterd by a reader for the first time. We, therefore, encourage 
readers who are not familiar with the Cavalieri integral to rather first read Section~\ref{??} instead. The reader should only refer back to the definitions 
presented in this sections when things in Section~\ref{??} become unclear. Moreover, the definitions presented below were taken from [?]. Furthermore, none of the theorems in this section are proved, the proofs can be found in [].

@@

\begin{theorem}
The function $g(x)$ is equal to $h^{-1}(x)$.
\end{theorem}

@@

\begin{theorem}
The following Cavalieri, Riemann, and Riemann--Stieltjes integrals are equivalent
\begin{equation}
\int_{a(y)}^{b(y)} f(x) dx = \int_a^b f\circ h(x) dx = \int_{a'}^{b'} f(x)dg(x). 
\end{equation}
\end{theorem}

>>>>

 \title[VISUALIZATION OF FRACTIONAL INTEGRALS]{VISUALIZATION OF THE RIEMANN-LIOUVILLE FRACTIONAL INTEGRAL \\ [3pt] IN ``FCAA'' JOURNAL}
 \author[\normalsize V. Kiryakova, S. Author]{\normalsize Virginia Kiryakova $^1$, Second Author $^2$}

@@

Ackerman et al. used the notion of non-rectangular integration strips to define the so called Cavalieri integral. The area of a non-rectangular 
integration strip is calculated using Cavalieri's principle. Cavalieri's principle is stated below without proof:
\begin{theorem}
Suppose two regions in a plane are included between two parallel lines in that plane. If every line parallel to these
two lines intersects both regions in line segments of equal length, then the two regions have equal areas. NEED CITATION
\end{theorem}
The definition of the Cavalieri integral is presented in Definition~\ref{def:cav_integral}.
It is, however, our experience that Definition~\ref{def:cav_integral} is hard to assimilate if it is encounterd by a reader for the first time. We, therefore, encourage 
readers who are not familiar with the Cavalieri integral to rather first read Section~\ref{??} instead. The reader who is not familiar with the Cavalieri integral should only refer back to the definitions 
presented in this section when things in Section~\ref{??} become unclear. Moreover, the definitions presented below were taken from [?]. Furthermore, none of the theorems in this section are proved, the proofs can be found in [].

@@

\begin{theorem}
\label{t:inv}
The function $g(x)$ is equal to $h^{-1}(x)$.
\end{theorem}

@@

\begin{theorem}
\label{t:conv}
The following Cavalieri, Riemann, and Riemann--Stieltjes integrals are equivalent
\begin{equation}
\int_{a(y)}^{b(y)} f(x) dx = \int_a^b f\circ h(x) dx = \int_{a'}^{b'} f(x)dg(x). 
\end{equation}
\end{theorem}

\section{Cavalieri Integral: Clarifying Example}
\label{sec:cav_integral_example}
The example which we present below was taken from \cite{?}. Let the region $R$ be bounded by the $x$-axis and the lines $f(x)=x$, $a(y)=1-y$ and $b(y)=4-y$. This region is depicted in Fig.~\ref{fig:caval2}.\\
%\begin{figure}[htb]
%\centering
%\includegraphics[width=0.3\textwidth]{fig12}
%\caption{Region bounded by the $x$-axis and the lines $f(x)=x$, $a(y)=1-y$, and $b(y)=4-y$. Reproduced from Quaestiones Mathematicae (2012) 35: 265-296 with permission \copyright~ NISC (Pty) Ltd.}
%\label{fig:ex1}
%\end{figure}
\begin{figure}[htb]
\centering
\includegraphics[width=0.75\textwidth]{fig13.pdf}
\caption{Region bounded by the $x$-axis and the lines $f(x)=x$, $a(y)=1-y$, and $b(y)=4-y$. In the case of $R$: $a=1$, $b=4$, $a'=\frac{1}{2}$ and $b'=2$. The figure also depicts the partition points $x_i^2$ as used in the Cavalieri sum (see Equation~\eqref{eq:cav_sum}). Reproduced from Quaestiones Mathematicae (2012) 35: 265-296 with permission \copyright~ NISC (Pty) Ltd.}
\label{fig:caval2}
\end{figure}

%\noindent
%The area of $R$ can be determined as follows if we employ the classical notion of integration:
%\begin{equation}
%\int_0^2x\, dx+\int_2^44-x\, dx- \int_0^{\frac{1}{2}}x\, dx-\int_{\frac{1}{2}}^11-x\, dx = 3.75. 
%\end{equation}

The area of $R$ can be approximated by summing together the area of rectangular integrations strips that inscribe $R$. There, however, exist a more 
straightforward way in which we can approximate the area of $R$: we can sum together the area of non-rectangular integration strips inscribing $R$. This alternative approach 
will only succeed it the sides of the aforementioned integration strips are all tranlsations of the function $a(y)$.

Let us express this idea more formally. Let $(x_i^1)_{i=0}^{n}$ denote a partition on the $x$-axis, such that $a = x_0^1 < x_1^1 < \cdots < x_n^1 = b$, and $\Delta x_i^1 = x_{i+1}^1 - x_i^1$.
We are now able to construct the following lower Cavalieri sum (Equation~\ref{eq:c_low}):
\begin{equation}
\label{eq:cav_sum}
\sum_{i=0}^{n-1} f(x_i^2)\Delta x_i^1.
\end{equation}
The partition points $(x_i^2)_{i=0}^{n}$ are depicted in Fig.~\ref{fig:caval2}. Cavalieri's principle tells us that the area of integration strip $i$ is equal to $f(x_i^2)\Delta x_i^1$. Equation.~\eqref{eq:cav_sum}, therefore, approximates the area of $R$. In the limit Eq.~\eqref{eq:cav_sum} approaches 
the Cavalieri integral (Definition~\ref{def:cav_integral}):
\begin{equation}
\label{eq:caval1}
\int_{a(y)}^{b(y)}f(x)\, dx = \lim_{n\to \infty}\sum_{i=0}^{n-1} f(x_i^2)\Delta x_i^1.
\end{equation}
It is, however, quite hard to evaluate the above integral directly. Fortunately, it is easy to convert a Cavalieri integral into an equivalent Riemann or Riemann-Stieltjes 
integral by using the functions $h$ and $g$ (Theorem~\ref{t:conv}). Expressed mathematically:
\begin{equation}
\label{eq:main_cav}
\int_{a(y)}^{b(y)}f(x)\,dx =\int_a^b f \circ h (x)\, dx = \int_{a'}^{b'} f(x) dg(x).
\end{equation}
We can calculate $g$ as follows (Definition~\ref{def:g}):
\begin{equation}
g(x) = x - a\circ f(x) + a.
\end{equation}
Moreover, $h=g^{-1}$ (Theorem~\ref{t:inv}). We can now evaluate the Cavalieri integral by using its equivalent Riemann or Rieman-Stieltjes integral.
If we use its Riemann equivalent we obtain:
\begin{equation}
\int_{a(y)}^{b(y)}f(x)\, dx = \int_a^b f \circ h (x)\, dx = \dfrac{1}{2}\int_1^4x\, dx = 3.75.  
\end{equation}
If we use its Riemann-Stieltjes equivalent we obtain:
\begin{equation}
\int_{a(y)}^{b(y)}f(x)\, dx = \int_{a'}^{b'} f \, dg(x) = \int_{\frac{1}{2}}^2x\, d2x = 3.75.  
\end{equation}

\noindent
Conversely, if $g$ is known (and not $a(y)$) and $g(a') = a$ then we can calculate $a(y)$ using the following \cite{grobler19}:
\begin{equation}
\label{eq:a_y}
a(y) = f^{-1}(y) - g\circ f^{-1}(y) + g(a'). 
\end{equation}
Eq.~\eqref{eq:a_y} allows us to transform a Riemann-Stieltjes integral into an equivalent Cavalieri integral. 
Furthermore, this transformation enables us to assign a geometric interpretation to a Riemann-Stieltjes integral. The interpretation being:
it represents the area obtained by summing together the area of an infinite number of non-rectangular infinitesimals; all of them being translations of $a(y)$. Note,
$b(y) = a(y) + (b-a)$.
